### Quick Start

This is a quick version of everything listed below, if you want more clear or specfic instructions then please skip this chaper and follow the steps in the following one. 

#### Set Up

In the `Console` tab of RStudio in `(None)` project: 

```{r b1, eval=FALSE}
install.packages("workflowr")
library("workflowr")
wflow_git_config(user.name = "First Last", user.email = "first.last@agios.com")
```

#### Creating Projects

In the `Console` tab, 

```{r b2, create, eval=FALSE}
wflow_start("PROJECT_NAME")
wflow_build()
wflow_publish(c("analysis/*.Rmd"), "Publish the initial files for PROJECT_NAME")
```

#### Connecting to GitLab

In the `Console` tab, 

```{r b3, git, eval=FALSE}
wflow_use_gitlab(username = "first.last", repository = "PROJECT_NAME", domain = "ceres.agios.com")
```

Go to GitLab and do the following:

+ Create a project in GitLab should the same name as the project in RStudio
    + We called ours PROJECT_NAME
+ Go back to GitLab and and scroll down to the push an existing Git repository option
    + Then, copy every thing in the box besides the cd line
+ Paste what you just copied into the `Terminal` tab in RStudio
    + Make sure you are in  PROJECT_NAME directory 


#### Creating a New File

In the `Console` tab, 

```{r b4, eval=FALSE}
wflow_open("analysis/NEW_FILE.Rmd")
wflow_build()
wflow_publish(c("analysis/*.Rmd"), "Publish the file NEW_FILE")
```

In the `Terminal` tab, 
```{r b5, eval=FALSE}
git push
```

#### Publish to GitLab without Rebuilding Sites

1. Edit the Rmd file and save
2. Run one of the following commands (doesn't matter)
    + wflow_build()
        + It does't matter if we build other files, they won't be added to git unless we add them in the next step
    + wflow_build("file.rmd")
    + Knit the file
3. `wflow_git_commit("file.rmd", "This is your commit message")`
4. Flip into the terminal and run `git push()`
      

